\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
Fix some mistakes.

In order to get a different view of how well our optimization was
performing, we annotated IonMonkey to emit for each addition
instruction compiled whether or not range analysis proved that it
could not overflow, and ran this against all of the tests in Kraken,
Sunspider, and v8bench. The data from these tests are presented in Figure
\ref{fig:count} (tests that were found to have very few total add
instructions were not included).

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.98\textwidth]{counts_graph.png}
\caption{Percentage of add overflow checks eliminated}
\label{fig:count}
\end{figure*}

@@

On a suite of standard Javascript benchmarks, our range analysis
succeeds in eliminating a large fraction of overflow checks for
integer additions. This translates into a minor overall performance
win on the Kraken benchmark suite and a very minor overall performance
loss on the Sunspider suite. Since we should only increase the
quality of the generated code, any performance losses should be from
increased compilation overhead (Sunspider tests in particular are
quite short). The performance improvements are decent, but not
stellar; we believe this is because Javascript code is generally not
integer-arithmetic-heavy tight loops and because the overflow test
branches are generally predicted correctly.

>>>>

In order to get a different view of how well our optimization was
performing, we annotated IonMonkey to emit for each addition and subtraction
instruction compiled whether or not range analysis proved that it
could not overflow, and ran this against all of the tests in Kraken,
Sunspider, and v8bench. The data from these tests are presented in Figure
\ref{fig:count} (tests that were found to have very few total add
instructions were not included).

@@

\begin{figure*}[!ht]
\centering
\includegraphics[width=0.98\textwidth]{counts_graph.png}
\caption{Fraction of add/subtract overflow checks eliminated}
\label{fig:count}
\end{figure*}

@@

On a suite of standard Javascript benchmarks, our range analysis
succeeds in eliminating a large fraction of overflow checks for
integer additions and subtractions. This translates into a minor
overall performance win on the Kraken benchmark suite and a very minor
overall performance loss on the Sunspider suite. Since we should only
increase the quality of the generated code, any performance losses
should be from increased compilation overhead (Sunspider tests in
particular are quite short). The performance improvements are decent,
but not stellar; we believe this is because Javascript code is
generally not integer-arithmetic-heavy tight loops and because the
overflow test branches are generally predicted correctly.
